\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Pass over 6, 6.1

\heading{Highlights}
In this paragraph we summarize results for \ttt{--width=16}, but \sys's evaluation reports on varying \ttt{width}s.
Overall, \sys accelerates 49/54 scripts by \todo{1.92--61.1}$\times$; % Eurosys: results for 16!!
  for the rest, the parallel performance is comparable to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
For a subset of our benchmarks~\sx{ours}, we decouple the speedup due \sys's DFG transformations alone from the one due to its runtime primitives:
  the former averages \todo{$9.3\times$}, jumping to \todo{$13.2\times$} due to the latter.
A different subset ($30$ benchmarks) sees average speedups of $6.02\times$~\sx{unix50}.
% , depending on the classed of commands involved
Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys significantly outperforms \ttt{sort --parallel}, which involves hand-tuning by its command developers, and performs better than GNU \ttt{parallel}, which returns incorrect results if used without care~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,

Using \sys's standard library of annotations for POSIX and GNU commands~\sx{parallelizability}, the vast majority of programs ($>50$, with $>200$ commands) require no effort to parallelize other than invoking \sys;
  only 6 ($<3\%$) commands, outside this library, needed a single-record annotation~\sx{macro2}.

In terms of correctness, \sys's results on multi-GB inputs are identical to the sequential ones.
Scripts feature ample opportunities for breaking semantics~\sx{micro}, which \sys avoids.
%% In one case, \sys avoids transforming a cycle (\ie a fragment whose input and output identifiers are the same).
%in another, it preserves the semantics that another parallelization command breaks.

@@

We evaluate \sys on popular, common, or classic \unix pipeline patterns~\cite{bentley1985spelling, bentley1986literate, taylor2004wicked}.
The goal is to evaluate performance benefits due to \sys's  
  (i) DFG transformations alone, including how \ttt{--width} affects speedup, 
  (ii) runtime primitives, showing results for several configurations of the runtime lattice (Fig.~\ref{fig:lattice}).

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for \ttt{width=} 2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
}
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

\heading{Programs}
%>\kk{How can we include a result for grep-light?  This is the IO
%>  intensive CPU-light grep. \sys has no speedup but also no slowdown
%>  (even if it IO heavy). Should we just mention that in text in
%>  passing?}
%>
%>\kk{Remember to mention that for spell and bigrams we dont show other
%>  parallel because they are all close to 1 (no speedup).}
Tab.~\ref{tab:eval} summarizes the first collection of programs.
%  shown in Fig.~\ref{fig:microbenchmarks}, which in turn reports on their performance characteristics.
NFA-Regex and Filter are in \sta, with the former centered around an expensive \todo{NFA-based} backtracking expression and the latter being an IO-intensive script.
% a DFA-based regular expression matching phase;
 % while the \unix \ttt{grep} command defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
Sort is a short script centered around a \pur command.
Wf and Top-n are based on McIlroy's classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
% \tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
%   it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
Spell, based on the original \ttt{spell} developed by Johnson~\cite{bentley1985spelling}, is another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in a dictionary.
Shortest-scripts extracts the 15 shortest scripts in the user's \ttt{PATH}, using the \ttt{file} utility and a higher-order \ttt{wc} via \ttt{xargs}~\cite[pg. 7]{taylor2004wicked}.
Diff and Set-diff compare streams via a \ttt{diff} (in \npu, non-parallelizable) and \ttt{comm} (in \pur), respectively.
Sort-sort uses consecutive \pur commands without interleaving them with commands that condense their input size (\eg \ttt{uniq}).
Finally, the two Bi-grams replicate and shift a stream by one entry to calculate bigrams, but Bi-gram-opt's groups 5 commands into one \pur command that has a more efficient $map$ and $aggregate$ implementation.

@@

Plots hide lines for configurations that lead to identical parallel programs.
There are two types of such cases (that appear in \todo{five} plots).
In the first type, \emph{Pash} (blue) and \emph{Pash-w/o-split} (red, hidden) lines are identical when \sys adds no \ttt{split} because the DFG width remains constant for the whole program;
  conversely, if both lines are shown, \ttt{split}s are needed due to changes in parallelism width and result in performance improvements.
In the second type, No Eager (green), Blocking Eager (orange), and \emph{Pash w/o Split} (red) are identical 
  because the program features a command in \pur relatively early.
This command requires an \ttt{agg}regator, whose output is of width 1, and beyond which non-\ttt{split} configurations are sequential (and see no speedup).
Conversely, all three lines exist when the width remains above 1 for the full program.
% needing a \ttt{split} to regain width.

Tab.~\ref{tab:eval} shows that \sys's transformation time is negligible, and its COST~\cite{mcsherryscalability} is 2. %  for all benchmarks.
Filter and Bigrams-opt, not in Fig.~\ref{fig:microbenchmarks}, achieve speedups of 1.5--2.5$\times$ and 2--30$\times$.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

\heading{Discussion}
% TODO: Add
% * \ttt{width}
% * why blocking is less than no eager
As expected, scripts with commands only in \sta get linear speedup.
\sys's \ttt{split} benefits scripts with \tpur or \tnpu commands, without negative effects on the rest.
Its \ttt{eager} primitive improves over Eager and Blocking-eager for all scripts.
% Blocking eager: data parallelism, but no task parallelism; No eager: blocking FIFO does not allow pushing -> underutilize CPU
\emph{Blocking Eager} is usually slower than \emph{No Eager} due to \ttt{agg}regators that read multiple input streams at the same time---\eg \ttt{sort -m}.
Sort-sort illustrates the full spectrum of primitives:
  (iii) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} while maintaining task parallelism
  (iv) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.

@@

As described earlier, \sys often achieves the maximum possible speedup % \ie without unnecessary process spawns and context switches, 
  in \ttt{width} that is lower than the number of available cores---\ie \ttt{width=}16--32 for a 64-core system.
This is also because \sys's runtime primitives spawn new processes---\eg Sort with \ttt{width=}8 spawns 37 processes:
  8 \ttt{tr}, 8 \ttt{sort}, 7 \emph{aggregation}, and 14 \ttt{relay} processes.

\todo{standard vs non-standard Bigrams}

@@

\heading{Take-aways}
\sys accelerates scripts by 4--60$\times$, depending on the commands involved.
Its runtime constructs improve over the baseline speedup achieved by its transformations.

@@

\heading{Program}
This program is inspired by Hadoop's Definitive Guide~\cite[\S2]{hadoop:15}, where it exemplifies a realistic analytics pipeline comprising 3 stages:
  fetch NOAA data (shell), convert them to a Hadoop-friendly format (shell), and calculate the maximum temperature (Hadoop).
While the book focuses only on the last stage, \sys parallelizes the entire pipeline.
% Only the last one is the real focus of the book, % demonstrating the benefits of using distributed framework such as Hadoop.
%   whereas we consider the entire pipeline. % ---from fetching data to outputting the maximum temperature.
% The version used in the evaluation is slightly different than the one presented in Fig.~\ref{fig:example} (14 stages and totalling 240 characters), simplified only for clarity of exposition, in that it expresses the \ttt{for} loop as a first stage followed by \ttt{xargs}.

@@

\heading{Take-aways}
\sys can be applied to programs of notable size \todo{and complexity} to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive, \ie the usual focus of conventional parallelization systems.

@@

% This section attempts to compare \sys with best-of-breed alternatives for particular taks.
As there are no prior systems directly comparable to \sys, we now draw comparisons with two specialized cases that excel within smaller fragments of \sys's proposed domain.

\pichskip{15pt}% Horizontal gap between picture and text
\parpic[r][t]{%
  \begin{minipage}{40mm}
    \includegraphics[width=\linewidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}%
    %% \captionof{figure}{This is a tiger.}
  \end{minipage}
}
\heading{Parallel Sort}
%% \kk{Explain what is the purpose of the
%%   microbenchmark. We want to establish that \sys scalability is as
%%   good as it could be.}
We first compare a GNU \ttt{sort} parallelized by \sys ($S_{PaSh}$) \vs the same \ttt{sort} with the 
%% \begin{wrapfigure}[10]{r}{0.25\textwidth}
%%   \centering
%%   %% \begin{center}
%%     \includegraphics[width=0.25\textwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
%%   %% \end{center}
%% %   \vspace{-15pt}
%% % \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.} }
%% \end{wrapfigure}
\ttt{--parallel} flag set ($S_{GNU}$). % , shown on the side.
% The results are shown on the side-figure below.
While \ttt{--parallel} is not a general solution, the comparison serves to establish a baseline for \sys.
$S_{GNU}$'s parallelism is configured to $2\times$ that of \todo{$S_{PaSh}$'s} \ttt{--width} (\ie the rightmost plot point for $S_{GNU}$ is for \ttt{--parallelism=128}), 
to account for \sys's additional runtime processes.
% and as such we note that the measurements are harsh for \sys.

@@

\heading{GNU Parallel}
We compare \sys to \ttt{parallel} (v.20160422), a GNU utility for running other commands in parallel~\cite{Tange2011a}, on a small bio-informatics script.
% Using its \ttt{--jobs} flag, we  redirect input from a file to 
% 554 / 330 
Sequential execution takes 554.8s \vs \sys's 128.5s (4.3$\times$), with most of the overhead coming from a single command---\ttt{cutadapt}.

>>>>

\heading{Highlights}
In this paragraph we summarize results for \ttt{--width=16}, but \sys's evaluation reports on varying \ttt{width}s.
Overall, \sys accelerates 47/52 scripts by 1.92--17.42$\times$; % Eurosys: results for 16!! \kk{I added them}
  for the rest, the parallel performance is comparable to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
  % \kk{eurosys: I have an issue that I am not sure how to address. I would like to have the 61.1x here (which is due to 64 width)  but I don't see a good way of including it without sounding suspicious.}
For a subset of our benchmarks~\sx{ours}, we decouple the speedup due to \sys's DFG transformations alone from the one achieved when including its runtime primitives:
  the former averages $5.9\times$, jumping to $8.6\times$ due to the latter.
A different subset ($30$ benchmarks) sees average speedups of $6.02\times$~\sx{unix50}.
% , depending on the classed of commands involved
Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands written in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys significantly outperforms \ttt{sort --parallel}, a hand-tuned parallel implementation, and performs better than GNU \ttt{parallel}, which returns incorrect results if used without care~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,

Using \sys's standard library of annotations for POSIX and GNU commands~\sx{parallelizability}, the vast majority of programs ($>50$, with $>200$ commands) require no effort to parallelize other than invoking \sys;
  only 6  ($<3\%$) commands, outside this library, needed a single-record annotation.

In terms of correctness, \sys's results on multi-GB inputs are always identical to the sequential.
Scripts feature ample opportunities for breaking semantics, which \sys avoids.
%% In one case, \sys avoids transforming a cycle (\ie a fragment whose input and output identifiers are the same).
%in another, it preserves the semantics that another parallelization command breaks.

@@

We first evaluate \sys on a set of popular, common, and classic \unix pipeline patterns~\cite{bentley1985spelling, bentley1986literate, taylor2004wicked}.
The goal is to evaluate performance benefits due to \sys's  
  (i) DFG transformations alone, including how \ttt{--width} affects speedup, and
  (ii) runtime primitives, showing results for several configurations of the runtime lattice (Fig.~\ref{fig:lattice}).

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for \ttiny{width=} 2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
}
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

\heading{Programs}
%>\kk{How can we include a result for grep-light?  This is the IO
%>  intensive CPU-light grep. \sys has no speedup but also no slowdown
%>  (even if it IO heavy). Should we just mention that in text in
%>  passing?}
%>
%>\kk{Remember to mention that for spell and bigrams we dont show other
%>  parallel because they are all close to 1 (no speedup).}
Tab.~\ref{tab:eval} summarizes the first collection of programs.
%  shown in Fig.~\ref{fig:microbenchmarks}, which in turn reports on their performance characteristics.
NFA-Regex is centered around an expensive \todo{NFA-based} backtracking expression and all of its commands are in \sta.
% and the latter being an IO-intensive script.
% a DFA-based regular expression matching phase;
 % while the \unix \ttt{grep} command defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
Sort is a short script centered around a \pur command.
Wf and Top-n are based on McIlroy's classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
% \tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
%   it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
Spell, based on the original \ttt{spell} developed by Johnson~\cite{bentley1985spelling}, is another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in a dictionary.
Shortest-scripts extracts the 15 shortest scripts in the user's \ttt{PATH}, using the \ttt{file} utility and a higher-order \ttt{wc} via \ttt{xargs}~\cite[pg. 7]{taylor2004wicked}.
Diff and Set-diff compare streams via a \ttt{diff} (in \npu, non-parallelizable) and \ttt{comm} (in \pur), respectively.
Sort-sort uses consecutive \pur commands without interleaving them with commands that condense their input size (\eg \ttt{uniq}).
Finally, Bi-grams replicates and shifts a stream by one entry to calculate bigrams.
% , but Bi-gram-opt's groups 5 commands into one \pur command that has a more efficient $map$ and $aggregate$ implementation.

@@

Plots do not include lines for configurations that lead to identical parallel programs.
There are two types of such cases. %  (that appear in \todo{five} plots).
In the first, \emph{Pash} (blue) and \emph{Pash-w/o-split} (red, hidden) lines are identical for scripts that \sys does not add any \ttt{split} since the width of the DFG is constant;
%  when \sys adds no \ttt{split} because the DFG width remains constant for the whole program;
  conversely (for spell, bi-grams, and sort), when both lines are shown, \sys has added \ttt{split}s due to changes in the DFG width (e.g. due to a \npu command).
In the second type, \emph{Pash w/o Split} (red) is identical to No Eager (green, hidden) and Blocking Eager (orange, hidden) because the input script features a command in \pur or \npu relatively early.
This command requires an \ttt{agg}regator, whose output is of width 1, and beyond which non-\ttt{split} configurations are sequential (and see no speedup).
% Conversely, all three lines exist when the width remains above 1 for the full program.
% needing a \ttt{split} to regain width.

Finally, Tab.~\ref{tab:eval} shows that \sys's transformation time is negligible, and its COST~\cite{mcsherryscalability} is 2. %  for all benchmarks.
% Filter and Bigrams-opt, not in Fig.~\ref{fig:microbenchmarks}, achieve speedups of 1.5--2.5$\times$ and 2--30$\times$.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

\heading{Discussion}
% TODO: Add
% * \ttt{width}
% * why blocking is less than no eager
As expected, scripts with commands only in \sta get linear speedup.
\sys's \ttt{split} benefits scripts with \tpur or \tnpu commands, without negative effects on the rest.
Its \ttt{eager} primitive improves over Eager and Blocking-eager for all scripts.
% Blocking eager: data parallelism, but no task parallelism; No eager: blocking FIFO does not allow pushing -> underutilize CPU
\emph{No Eager} is usually faster than \emph{Blocking Eager} 
% due to \ttt{agg}regators that read multiple input streams at the same time---\eg \ttt{sort -m}.
% \kk{eurosys: while the above is technically true, it is a bit difficult to explain here, so I prefer the sentence below.}
since it allows its producer and consumer to execute in parallel.
Sort-sort illustrates the full spectrum of primitives:
  (i) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} 
  % while maintaining task parallelism
  (ii) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.

@@

As described earlier, \sys often achieves the maximum possible speedup % \ie without unnecessary process spawns and context switches, 
  for a \ttt{width} that is lower than the number of available cores---\ie \ttt{width=}16--32 for a 64-core system.
This is also because \sys's runtime primitives spawn new processes---\eg Sort with \ttt{width=}8 spawns 37 processes:
  8 \ttt{tr}, 8 \ttt{sort}, 7 \emph{aggregation}, and 14 \ttt{relay} processes.

% \todo{standard vs non-standard Bigrams}

@@

\heading{Take-aways}
\sys accelerates scripts by up to 60$\times$, depending on the commands involved.
Its runtime constructs improve over the baseline speedup achieved by its transformations.

@@

\heading{Program}
This program is inspired by Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}, where it exemplifies a realistic analytics pipeline comprising three sub-tasks:
  fetch data from NOAA (shell), convert them to a Hadoop-friendly format (shell), and calculate the maximum temperature (Hadoop).
While the book focuses only on the last one, \sys parallelizes the entire pipeline.
% Only the last one is the real focus of the book, % demonstrating the benefits of using distributed framework such as Hadoop.
%   whereas we consider the entire pipeline. % ---from fetching data to outputting the maximum temperature.
% The version used in the evaluation is slightly different than the one presented in Fig.~\ref{fig:example} (14 stages and totalling 240 characters), simplified only for clarity of exposition, in that it expresses the \ttt{for} loop as a first stage followed by \ttt{xargs}.

@@

\heading{Take-aways}
\sys can be applied to programs of notable size \todo{and complexity} to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive regions, \ie the usual focus of conventional parallelization systems.

@@

% This section attempts to compare \sys with best-of-breed alternatives for particular taks.
As there are no prior systems directly comparable to \sys, this section draws comparisons with two specialized cases that excel within smaller fragments of \sys's proposed domain.

\pichskip{15pt}% Horizontal gap between picture and text
\parpic[r][t]{%
  \begin{minipage}{40mm}
    \includegraphics[width=\linewidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}%
    %% \captionof{figure}{This is a tiger.}
  \end{minipage}
}
\heading{Parallel Sort}
%% \kk{Explain what is the purpose of the
%%   microbenchmark. We want to establish that \sys scalability is as
%%   good as it could be.}
We first compare a single GNU \ttt{sort} parallelized by \sys ($S_{PaSh}$) \vs the same \ttt{sort} with the 
%% \begin{wrapfigure}[10]{r}{0.25\textwidth}
%%   \centering
%%   %% \begin{center}
%%     \includegraphics[width=0.25\textwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
%%   %% \end{center}
%% %   \vspace{-15pt}
%% % \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.} }
%% \end{wrapfigure}
\ttt{--parallel} flag set ($S_{GNU}$). % , shown on the side.
% The results are shown on the side-figure below.
While \ttt{--parallel} is not a general solution, the comparison serves to establish a baseline for \sys.
$S_{GNU}$'s parallelism is configured to $2\times$ that of \todo{$S_{PaSh}$'s} \ttt{--width} (\ie the rightmost plot point for $S_{GNU}$ is for \ttt{--parallelism=128}), 
to account for \sys's additional runtime processes.
% and as such we note that the measurements are harsh for \sys.

@@

\heading{GNU Parallel}
We compare \sys to \ttt{parallel} (v.20160422), a GNU utility for running other commands in parallel~\cite{Tange2011a}, on a small bio-informatics script.
% Using its \ttt{--jobs} flag, we  redirect input from a file to 
% 554 / 330 
Sequential execution takes 554.8s \vs \sys's 128.5s (4.3$\times$), with most of the overhead coming from \todo{a single command}.
